---
title: "Carbon Flux in Boreal Forests"
format: html
server: shiny
---

*Explanatory Variable Descriptions:*

Temperature: Air temperature, measured at tower

Shortwave Radiation: Incoming solar radiation, measured at tower

Net Radiation: Net incoming minus outgoing radiation, measured at tower

Vapor Pressure Deficit: Deficit of moisture in the air relative to amount holdable when saturated, measured at tower

Precipitation: Average daily precipitation within the timestep, measured at tower

Evapotranspiration: Measure of how much water is lost through evaporation and transpiration, calculated from latent heat fluxes measured at tower

PPFD: Photosynthetic Photon Flux Density, a measure of how many photons within the photosynthetically active wavelengths are reaching the plants, measured at tower

NDVI: (Only available at 16 day resolution) Measure of how green the plants are, measured by satellite


*Carbon Flux Variable Descriptions*

NEE: Net ecosystem exchange, the carbon flux directly measured by the tower. NEE = RECO - GPP, and is negative when the ecosystem is a carbon sink and positive when the ecosystem is a carbon source

GPP: Amount of photosynthesis (carbon sink) in the ecosystem; derived from NEE by nighttime partitioning method

RECO: Amount of respiration (carbon source) in the ecosystem; derived from NEE by nighttime partitioning method



*Usage Notes*

Due to an annoying bug, you must click on the first tab (Variable vs Flux by Site) before being able to switch to any other tab. 

```{r}
#| context: setup
#| include: false
library(bslib)
library(rsconnect)
```

```{r} 
#| context: setup
#| include: false
# Read in all data
library(tidyverse)
library(lubridate)
library(stringr)
library(ggtext)

resolution <- "WW"

sites <- c("CA-NS1", "CA-NS2", "CA-NS3", "CA-NS4", "CA-NS5", "CA-NS6", "CA-NS7")

CA_NS1 <- tibble(read.csv(str_c("Data/",sites[1],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS2 <- tibble(read.csv(str_c("Data/",sites[2],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS3 <- tibble(read.csv(str_c("Data/",sites[3],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS4 <- tibble(read.csv(str_c("Data/",sites[4],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS5 <- tibble(read.csv(str_c("Data/",sites[5],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS6 <- tibble(read.csv(str_c("Data/",sites[6],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS7 <- tibble(read.csv(str_c("Data/",sites[7],"/", resolution,".csv"),
                               na.strings = "-9999"))

WW_data <- bind_rows(list("CA-NS1" = CA_NS1,"CA-NS2" = CA_NS2,"CA-NS3" = CA_NS3,"CA-NS4" = CA_NS4,"CA-NS5" = CA_NS5,"CA-NS6" = CA_NS6,"CA-NS7" = CA_NS7), .id = "Site")


resolution <- "MM"

sites <- c("CA-NS1", "CA-NS2", "CA-NS3", "CA-NS4", "CA-NS5", "CA-NS6", "CA-NS7")

CA_NS1 <- tibble(read.csv(str_c("Data/",sites[1],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS2 <- tibble(read.csv(str_c("Data/",sites[2],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS3 <- tibble(read.csv(str_c("Data/",sites[3],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS4 <- tibble(read.csv(str_c("Data/",sites[4],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS5 <- tibble(read.csv(str_c("Data/",sites[5],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS6 <- tibble(read.csv(str_c("Data/",sites[6],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS7 <- tibble(read.csv(str_c("Data/",sites[7],"/", resolution,".csv"),
                               na.strings = "-9999"))

MM_data <- bind_rows(list("CA-NS1" = CA_NS1,"CA-NS2" = CA_NS2,"CA-NS3" = CA_NS3,"CA-NS4" = CA_NS4,"CA-NS5" = CA_NS5,"CA-NS6" = CA_NS6,"CA-NS7" = CA_NS7), .id = "Site")

resolution <- "DD"

sites <- c("CA-NS1", "CA-NS2", "CA-NS3", "CA-NS4", "CA-NS5", "CA-NS6", "CA-NS7")

CA_NS1 <- tibble(read.csv(str_c("Data/",sites[1],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS2 <- tibble(read.csv(str_c("Data/",sites[2],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS3 <- tibble(read.csv(str_c("Data/",sites[3],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS4 <- tibble(read.csv(str_c("Data/",sites[4],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS5 <- tibble(read.csv(str_c("Data/",sites[5],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS6 <- tibble(read.csv(str_c("Data/",sites[6],"/", resolution,".csv"),
                               na.strings = "-9999"))

CA_NS7 <- tibble(read.csv(str_c("Data/",sites[7],"/", resolution,".csv"),
                               na.strings = "-9999"))


DD_data <- bind_rows(list("CA-NS1" = CA_NS1,"CA-NS2" = CA_NS2,"CA-NS3" = CA_NS3,"CA-NS4" = CA_NS4,"CA-NS5" = CA_NS5,"CA-NS6" = CA_NS6,"CA-NS7" = CA_NS7), .id = "Site")


DD_data <- DD_data |> mutate(TIMESTAMP = ymd(str_c(str_sub(TIMESTAMP, 1, 4), 
                                                   str_sub(TIMESTAMP, 5, 6), 
                                                   str_sub(TIMESTAMP, 7, 8), sep = '-')))

WW_data <- WW_data |> mutate(TIMESTAMP = ymd(str_c(str_sub(TIMESTAMP_START, 1, 4), 
                                                   str_sub(TIMESTAMP_START, 5, 6), 
                                                   str_sub(TIMESTAMP_START, 7, 8), sep = '-')))

MM_data <- MM_data |> mutate(TIMESTAMP = ym(str_c(str_sub(TIMESTAMP, 1, 4), 
                                                  str_sub(TIMESTAMP, 5, 6), sep = '-')))

full_NDVI_data <- read.csv("Data/MODIS_NDVI_data.csv")
#note: currently ignores quality flags
NDVI_data <- full_NDVI_data |> select(ID, Date, MOD13A1_061__500m_16_days_NDVI) |> 
  rename(#"Site" = ID, 
         "NDVI" = MOD13A1_061__500m_16_days_NDVI) |>
  mutate(Date = ymd(Date))

DD_16 <- NDVI_data |>
  mutate(Date = as.Date(Date)) |>
  left_join(DD_data, by = join_by("Date" == "TIMESTAMP", "ID" == "Site"))

#Get evapotranspiration data
library(bigleaf)
WW_data <-WW_data |> mutate(ET = LE.to.ET(LE_F_MDS, TA_F), ET_QC = LE_F_MDS_QC)
MM_data <-MM_data |> mutate(ET = LE.to.ET(LE_F_MDS, TA_F), ET_QC = LE_F_MDS_QC)
DD_data <-DD_data |> mutate(ET = LE.to.ET(LE_F_MDS, TA_F), ET_QC = LE_F_MDS_QC)
```


```{r}
#| context: setup
#| include: false

#Get Global Functions
#Note; this won't work properly on HH data
#Replaces the NEE_VUT_REF values with NA when their QC is less than a threshold
filter_fluxes <- function(flux_df, QC_threshold){
  indexes_to_filter <- flux_df$NEE_VUT_REF_QC < QC_threshold
  flux_df$NEE_VUT_REF <- replace(flux_df$NEE_VUT_REF, indexes_to_filter, NA)
  return(flux_df)
}

filter_variables <- function(flux_df, QC_threshold,variables){
  for (variable in variables){
    if (substr(variable ,1,3) == "GPP" | substr(variable ,1,4) == "RECO"){
      #GPP and RECO don't have their own quality flags they just use the NEE one
      indexes_to_filter <- flux_df[,"NEE_VUT_REF_QC"] < QC_threshold
      flux_df[, variable] <- replace(flux_df[,variable], indexes_to_filter, NA)
    } else {
      indexes_to_filter <- flux_df[,paste(variable, "QC", sep = "_")] < QC_threshold
      flux_df[, variable] <- replace(flux_df[,variable], indexes_to_filter, NA)
    }
  }
  return(flux_df)
}

```



```{r}
#Set up UI

available_variables <- c("Temperature", "Shortwave Radiation", "Net Radiation", "Vapor Pressure Deficit", 
                         "Precipitation", "Evapotranspiration", "PPFD")

available_Yvariables <- c("NEE", "GPP", "RECO")


available_sites <- c("1850 Burn", "1930 Burn", "1964 Burn (dry)", "1964 Burn (wet)", "1981 Burn", "1989 Burn", "1998 Burn")

available_timescales <- c("Daily", "Weekly", "Monthly")

available_statistics <- c("Min", "Max", "Mean", "STD", "Flux Correlation", "Value With Max Flux", "Value With Min Flux",
                          "Flux Single Regression Slope", "Flux Multiple Regression Slope", 
                          "Flux Nearest Neighbor RSS")

available_timeseries <- c("NEE", "GPP", "RECO", "Temperature", "Shortwave Radiation", "Net Radiation", "Vapor Pressure Deficit", "Precipitation", "Evapotranspiration", "PPFD")

navset_card_underline(
  nav_panel("Variable vs Flux By Site. ", 
            card(card_body(
                "
                These plots allow you to investigate the relationship between a variable of your choice and NEE, GPP, or RECO
                at your desired timescale (default weekly) in scatterplot form. You can choose which site you want to display 
                in each of the two panels to do a side by side comparison. The nearest-neighbor smoothing averages of the 
                relationship between all sites is also shown.
                "
            )),
            layout_sidebar(
              sidebar = sidebarPanel(
                accordion(
                  open = c("Variables"),
                  accordion_panel(
                    "Variables",
                    radioButtons("chosenVariable", "Explanatory Variable", available_variables[-5], selected = "Temperature"),
                    radioButtons("chosenYVariable", "Carbon Flux Variable", available_Yvariables, selected = "NEE")
                  ),
                  accordion_panel(
                    "Site 1",
                    radioButtons("chosenSite1", "Site 1:", available_sites, selected = "1850 Burn")
                  ), 
                  accordion_panel(
                    "Site 2",
                    radioButtons("chosenSite2", "Site 2:", available_sites, selected = "1998 Burn")
                  ),
                  accordion_panel(
                    "Timescales",
                    radioButtons("chosenTimescale", "Temporal Resolution:", available_timescales, selected = "Weekly")
                  ))),
              accordion(
                accordion_panel(
                  "Comparative Site Scatterplots",
                  layout_columns(
                      plotOutput("Site1VarNEEScatterplot"),
                      plotOutput("Site2VarNEEScatterplot")
                )),
                accordion_panel(
                  "All Site Splines",
                  plotOutput("VarNEESplineplot")
                )
              ))),
  nav_panel("Variable Stats By Years Since Burn  ",
             card(card_body(
                "
                This plot allows you to investigate the relationship between some common stats about an investigated variable and the
                number of years since burn. These stats include the min, max, mean, and standard deviation of a single variable
                (daily scale). This also allows you to
                look at stats about the relationship between an investigated variable and a flux variable; including the value of the investigated variable at which the flux variable is maximum or minimum, the R^2 of the
                correlation between the investigated and flux variable, the slope of the regression line between the predictor and
                the flux variable (either single or multiple regression), and the RSS of the nearest neighbor regression line displayed in
                the Variable vs Flux by Site tab (a measure of how predictable flux is from that variable); all at the daily scale. 
                Additionally, you can see density plots for daily values of the investigated variable by site.
                "
            )),
            layout_sidebar(
              sidebar = sidebarPanel(
                accordion(
                  open = c("Stat Choice", "Variables"),
                  accordion_panel(
                    "Stat Choice",
                    radioButtons("chosenStat", "Statistic to Plot", available_statistics,
                                 selected = "Min")),
                  accordion_panel(
                    "Variables",
                    radioButtons("chosenVariable2", "Investigated Variable", append(available_variables, available_Yvariables),
                                 selected = "Temperature"),
                    radioButtons("chosenYVariable2", "Flux Variable", available_Yvariables, selected = "NEE")
                  ))),
              accordion(
                accordion_panel("Plot of Statistics",
                                plotOutput("StatPlot")),
                accordion_panel("Violin Plot",
                                plotOutput("ViolinPlot"))
              )
            )), ## THIS IS WHERE IM STARTING
    nav_panel("Variable Timeseries  ", 
            card(card_body(
                "
                These plots allow you to investigate the temporal pattern of a variable of your choice over a four-year time period
                at your desired timescale (default weekly) in scatterplot form. You can choose which site you want to display 
                in each of the two panels to do a side by side comparison. The nearest-neighbor smoothing averages of the 
                relationship between all sites is also shown.
                "
            )),
            layout_sidebar(
              sidebar = sidebarPanel(
                accordion(
                  open = c("Variables"),
                  accordion_panel(
                    "Variables",
                    radioButtons("chosenTimeseries_2", "Variable", available_timeseries, selected = "NEE")
                  ),
                  accordion_panel(
                    "Site 1",
                    radioButtons("chosenSite1_2", "Site 1:", available_sites, selected = "1850 Burn")
                  ), 
                  accordion_panel(
                    "Site 2",
                    radioButtons("chosenSite2_2", "Site 2:", available_sites, selected = "1998 Burn")
                  ),
                  accordion_panel(
                    "Timescales",
                    radioButtons("chosenTimescale_2", "Temporal Resolution:", available_timescales, selected = "Weekly")
                  ))),
              accordion(
                accordion_panel(
                  "Comparative Site Timeseries",
                  layout_columns(
                      plotOutput("Site1Timeseries"),
                      plotOutput("Site2Timeseries")
                )),
                accordion_panel(
                  "All Site Splines",
                  plotOutput("TimeseriesSmooth")
                )
              ))),
  nav_panel("NDVI vs Flux By Site", 
            card(card_body(
                "
                These plots allow you to investigate the relationship between NDVI and NEE, GPP, or RECO
                in scatterplot form. You can choose which site you want to display 
                in each of the two panels to do a side by side comparison. The nearest-neighbor smoothing averages of the 
                relationship between all sites is also shown.
                "
            )),
            layout_sidebar(
              sidebar = sidebarPanel(
                accordion(
                  open = c("Variables"),
                  accordion_panel(
                    "Variables",
                    radioButtons("chosenYVariable_3", "Carbon Flux Variable", available_Yvariables, selected = "NEE")
                  ),
                  accordion_panel(
                    "Site 1",
                    radioButtons("chosenSite1_3", "Site 1:", available_sites, selected = "1850 Burn")
                  ), 
                  accordion_panel(
                    "Site 2",
                    radioButtons("chosenSite2_3", "Site 2:", available_sites, selected = "1998 Burn")
                  ),
                )),
              accordion(
                accordion_panel(
                  "Comparative Site Scatterplots",
                  layout_columns(
                      plotOutput("Site1NDVIScatterplot"),
                      plotOutput("Site2NDVIScatterplot")
                )),
                accordion_panel(
                  "All Site Splines",
                  plotOutput("NDVISplineplot")
                )
              )))
)
```



```{r}
#| context: server

variables_names_to_ids <- c("Temperature" = "TA_F", "Shortwave Radiation" = "SW_IN_F", "Longwave Radiation" = "LW_IN_F",
                            "Net Radiation" = "NETRAD", "Vapor Pressure Deficit" = "VPD_F", "Pressure" = "PA_F", 
                            "Precipitation" = "P_F", "Wind Speed" = "WS_F", "Evapotranspiration" = "ET", "PPFD" = "PPFD_IN",
                            "NEE" = "NEE_VUT_REF", "GPP" = "GPP_NT_VUT_REF", "RECO" = "RECO_NT_VUT_REF", "NDVI" = "NDVI")
variables_ids_to_units <- c("TA_F" = "(ºC)", "SW_IN_F" = "(W/m^2)", "LW_IN_F" = "(W/m^2)",
                            "NETRAD" = "(W/m^2)", "VPD_F" = "(hPa)", "PA_F" = "(kPa)", 
                            "P_F" = "(mm/day)", "WS_F" = "(m/s)", "ET" = "(kg/m^2s", 
                            "PPFD_IN" = "(umolPhotons/m^2s)",
                             "NEE_VUT_REF" = "(gC/m^2day)", "GPP_NT_VUT_REF" = "(gC/m^2day)",  
                            "RECO_NT_VUT_REF" = "(gC/m^2day)")



sites_names_to_ids <- c("1850 Burn" = "CA-NS1", "1930 Burn" = "CA-NS2", "1964 Burn (dry)" = "CA-NS3", 
                        "1964 Burn (wet)" = "CA-NS4", "1981 Burn" = "CA-NS5", "1989 Burn" = "CA-NS6", "1998 Burn" = "CA-NS7")


sites_ids_to_names <- c("CA-NS1" = "1850 Burn", "CA-NS2" = "1930 Burn", "CA-NS3" = "1964 Burn (dry)", 
                        "CA-NS4" = "1964 Burn (wet)", "CA-NS5" = "1981 Burn", "CA-NS6" = "1989 Burn", "CA-NS7" = "1998 Burn")


filtering_threshold <- 0.8

site_colors <- c("CA-NS1" = "#f92104", "CA-NS2" = "#f9a600", "CA-NS3" = "#2df900", "CA-NS4" = "#00f9f9", 
                 "CA-NS5" = "#0031f9", "CA-NS6" = "#9202f9", "CA-NS7" = "#f902d8")

span_dist <- 0.4

data <- reactive({
  if (input$chosenTimescale == "Weekly"){
    data <- WW_data
  } else if (input$chosenTimescale == "Daily"){
    data <- DD_data
  } else {
    data <- MM_data
  }
  return(data)
})

Xscale <- reactive({
  data <- data()
  variable_id <- variables_names_to_ids[input$chosenVariable]
  min_val <- min(data[,variable_id], na.rm = T)
  max_val <- max(data[,variable_id], na.rm = T)
  range_val <- range(data[,variable_id], na.rm = T)[1] - range(data[,variable_id], na.rm = T)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

Yscale <- reactive({
  data <- data()
  yval <- variables_names_to_ids[input$chosenYVariable]
  min_val <- min(data[,yval], na.rm = T)
  max_val <- max(data[,yval], na.rm = T)
  range_val <- range(data[,yval], na.rm = T)[1] - range(data[,yval], na.rm = T)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

title_width <- 30

output$Site1VarNEEScatterplot <- renderPlot({
  
  variable_id <- variables_names_to_ids[input$chosenVariable]
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable]
  site_id = sites_names_to_ids[input$chosenSite1]
  
  
  siteData <- data() 
  siteData <- siteData |> filter(Site == site_id) |> 
                       filter_variables(0.8, c(Yvariable_id, variable_id))
  
  xlims <- Xscale()
  ylims <- Yscale()
  
  siteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(xlims[1],xlims[2]) + ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = paste(input$chosenVariable, variables_ids_to_units[variable_id]), 
                 y = paste(input$chosenYVariable, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Relationship between", input$chosenVariable, "and", input$chosenYVariable,
                               "at the", input$chosenSite1, "Site"), width = title_width)) + theme_classic()
})

output$Site2VarNEEScatterplot <- renderPlot({

  variable_id <- variables_names_to_ids[input$chosenVariable]
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable]
  site_id = sites_names_to_ids[input$chosenSite2]
  
  siteData <- data() |> filter(Site == site_id) |> 
                       filter_variables(0.8, c(Yvariable_id, variable_id))
  
  xlims <- Xscale()
  ylims <- Yscale()
  
  siteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(xlims[1],xlims[2]) + ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = paste(input$chosenVariable, variables_ids_to_units[variable_id]), 
                 y = paste(input$chosenYVariable, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Relationship between", input$chosenVariable, "and", input$chosenYVariable,
                               "at the", input$chosenSite2, "Site"), width = title_width)) + theme_classic()
})

output$VarNEESplineplot <- renderPlot({

  variable_id <- variables_names_to_ids[input$chosenVariable]
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable]
  
  variableData <- data() |> filter_variables(0.8, c(Yvariable_id, variable_id))
  
  variableData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id), color = Site)) +
            geom_smooth(se = T, alpha = 0.2, method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            scale_color_manual(labels = sites_ids_to_names, values = site_colors) +
            labs(x = paste(input$chosenVariable, variables_ids_to_units[variable_id]), 
                 y = paste(input$chosenYVariable, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Relationship between", input$chosenVariable, "and ",input$chosenYVariable," at all sites"), width = title_width)) +
    theme_classic()
})

```


```{r}
#| context: server

data2 <- reactive({
  if (input$chosenTimescale_2 == "Weekly"){
    data <- WW_data
  } else if (input$chosenTimescale_2 == "Daily"){
    data <- DD_data
  } else {
    data <- MM_data
  }
  return(data)
})


Xscale2 <- reactive({
  data <- data2()
  min_val <- min(data$TIMESTAMP)
  max_val <- max(data$TIMESTAMP)
  range_val <- range(data$TIMESTAMP)[1] - range(data$TIMESTAMP)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

Yscale2 <- reactive({
  data <- data2()
  yval <- variables_names_to_ids[input$chosenTimeseries_2]
  min_val <- min(data[,yval], na.rm = T)
  max_val <- max(data[,yval], na.rm = T)
  range_val <- range(data[,yval], na.rm = T)[1] - range(data[,yval], na.rm = T)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

output$Site1Timeseries <- renderPlot({
  
  variable_id <- 'TIMESTAMP'
  Yvariable_id <- variables_names_to_ids[input$chosenTimeseries_2]
  site_id = sites_names_to_ids[input$chosenSite1_2]
  
  
  siteData <- data2() 
  siteData <- siteData |> filter(Site == site_id) |> 
                       filter_variables(0.8, Yvariable_id)
  
  xlims <- Xscale2()
  ylims <- Yscale2()
  
  siteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(as.Date(xlims[1]),as.Date(xlims[2])) + 
            ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = 'Date', y = paste(input$chosenTimeseries_2, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Timeseries of", input$chosenTimeseries_2,
                               "at the", input$chosenSite1_2, "Site"), width = title_width)) + theme_classic()
})

output$Site2Timeseries <- renderPlot({
  
  variable_id <- 'TIMESTAMP'
  Yvariable_id <- variables_names_to_ids[input$chosenTimeseries_2]
  site_id = sites_names_to_ids[input$chosenSite2_2]
  
  
  siteData <- data2() 
  siteData <- siteData |> filter(Site == site_id) |> 
                       filter_variables(0.8, Yvariable_id)
  
  xlims <- Xscale2()
  ylims <- Yscale2()
  
  siteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(as.Date(xlims[1]),as.Date(xlims[2])) + 
            ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = 'Date', y = paste(input$chosenTimeseries_2, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Timeseries of", input$chosenTimeseries_2,
                               "at the", input$chosenSite2_2, "Site"), width = title_width)) + theme_classic()
})

output$TimeseriesSmooth <- renderPlot({

  variable_id <- 'TIMESTAMP'
  Yvariable_id <- variables_names_to_ids[input$chosenTimeseries_2]
  
  variableData <- data2() |> filter_variables(0.8, Yvariable_id)
  
  xlims <- Xscale2()
  ylims <- Yscale2()
  
  variableData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id), color = Site)) +
            geom_smooth(se = T, alpha = 0.2, method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            scale_color_manual(labels = sites_ids_to_names, values = site_colors) +
            labs(x = 'Date', y = paste(input$chosenTimeseries_2, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Timeseries of",input$chosenTimeseries_2,"at all sites"), width = title_width)) + theme_classic()
})

Xscale3 <- reactive({

  min_val <- min(DD_16$NDVI, na.rm = T)
  max_val <- max(DD_16$NDVI, na.rm = T)
  range_val <- range(DD_16$NDVI, na.rm = T)[1] - range(DD_16$NDVI, na.rm = T)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

Yscale3 <- reactive({

  yval <- variables_names_to_ids[input$chosenYVariable_3]
  min_val <- min(DD_16[,yval], na.rm = T)
  max_val <- max(DD_16[,yval], na.rm = T)
  range_val <- range(DD_16[,yval], na.rm = T)[1] - range(DD_16[,yval], na.rm = T)[2] 
  c(min_val - 0.1*range_val, max_val + .1*range_val)
})

output$Site1NDVIScatterplot <- renderPlot({
  
  variable_id <- "NDVI"
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable_3]
  site_id = sites_names_to_ids[input$chosenSite1_3]
  
  xlims <- Xscale3()
  ylims <- Yscale3()
  
  SiteData <- DD_16 |> filter(ID == site_id) |> 
                       filter_variables(0.8, Yvariable_id)
  

  
  SiteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(xlims[1],xlims[2]) + ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = 'NDVI', y = paste(input$chosenYVariable_3, variables_ids_to_units[Yvariable_id]), 
                 title = stringr::str_wrap(paste("Relationship between NDVI and", input$chosenYVariable_3 ,
                               "at the", input$chosenSite1_3, "Site"), width = title_width)) + theme_classic()
})

output$Site2NDVIScatterplot <- renderPlot({

  variable_id <- "NDVI"
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable_3]
  site_id = sites_names_to_ids[input$chosenSite2_3]
  
  xlims <- Xscale3()
  ylims <- Yscale3()
  
  SiteData <- DD_16 |> filter(ID == site_id) |> 
                       filter_variables(0.8, Yvariable_id)
  
  
  SiteData |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id))) +
            xlim(xlims[1],xlims[2]) + ylim(ylims[1],ylims[2]) +
            geom_point(alpha = 0.7, color = site_colors[site_id]) + 
            geom_smooth(se = F, color = "black", method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            labs(x = 'NDVI', y = paste(input$chosenYVariable_3, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Relationship between NDVI and", input$chosenYVariable_3,
                               "at the", input$chosenSite2_3, "Site"), width = title_width)) + theme_classic()
})

output$NDVISplineplot <- renderPlot({

  variable_id <- "NDVI"
  Yvariable_id <- variables_names_to_ids[input$chosenYVariable_3]
  

  
  DD_16 <- DD_16 |> filter_variables(0.8, Yvariable_id)

  
  DD_16 |> ggplot(aes(x = !!sym(variable_id), y = !!sym(Yvariable_id), color = ID)) +
            geom_smooth(se = T, alpha = 0.2, method = "loess", span = span_dist) + scale_alpha(guide = "none") +
            scale_color_manual(labels = sites_ids_to_names, values = site_colors) +
            labs(x = 'NDVI', y=paste(input$chosenYVariable_3, variables_ids_to_units[Yvariable_id]),
                 title = stringr::str_wrap(paste("Relationship between NDVI and",input$chosenYVariable_3,"at all sites"), width = title_width)) + theme_classic()
})

```



```{r}
#| context: server
#| include: FALSE

sites_ids_to_burntime <- c("CA-NS1" = 152, "CA-NS2" = 72, "CA-NS3" = 38, 
                        "CA-NS4" = 38, "CA-NS5" = 21, "CA-NS6" = 13, "CA-NS7" = 2)


available_variables <- c("Temperature", "Shortwave Radiation", "Net Radiation", "Vapor Pressure Deficit", 
                         "Precipitation", "Evapotranspiration", "PPFD")

get_stats <- reactive({
  
  years_since_burn = rep(0,7)
  site_ID = rep(0,7)
  min_val = rep(0,7) 
  max_val = rep(0,7)
  mean_val = rep(0,7)
  std_val = rep(0,7)
  val_of_max = rep(0,7)
  val_of_min = rep(0,7)
  correlation = rep(0,7)
  single_slope = rep(0,7)
  multiple_slope = rep(0,7)
  loess_RSS = rep(0,7)
  
  Xvar <- variables_names_to_ids[input$chosenVariable2]
  Yvar <- variables_names_to_ids[input$chosenYVariable2]
  
  index <- 1
  
  for (siteID in sites_names_to_ids) {
    years_since_burn[index] = sites_ids_to_burntime[siteID]
    site_ID[index] = siteID
    
    Xdata <- DD_data |> filter(Site == siteID) |> filter_variables(0.8, c(Xvar)) 
    Xdata <- Xdata[, c("TIMESTAMP", Xvar)] |> drop_na()
    days_of_year <- Xdata |> pull(var = TIMESTAMP) |> yday()
    Xdata <- Xdata |> mutate("DOY" = days_of_year)
    
    min_val[index] <- Xdata |> pull(var = Xvar) |> min()
    max_val[index] <- Xdata |> pull(var = Xvar) |> max()
    mean_val[index] <- Xdata |> pull(var = Xvar) |> mean()
    std_val[index] <- Xdata |> pull(var = Xvar) |> sd()
    
    
    BothData <-  DD_data |> filter(Site == siteID) |> filter_variables(0.8, c(Xvar, Yvar))
    
    max_ind <- BothData |> pull(var = Yvar) |> which.max()
    min_ind <- BothData |> pull(var = Yvar) |> which.min()
    vals <- BothData |> pull(var = Xvar)
    val_of_max[index] <- vals[max_ind]
    val_of_min[index] <- vals[min_ind]
    
    
    if (Xvar == Yvar){
      correlation[index] <- 1
      single_slope[index] <- 1
      multiple_slope[index] <- 1
      loess_RSS[index] <- 0
    } else {
    
      if (Xvar %in% variables_names_to_ids[available_variables]){
       AllData <- DD_data|> filter(Site == siteID) |> filter_variables(0.8, c(variables_names_to_ids[available_variables], Yvar)) 
       AllData <- AllData[,c(variables_names_to_ids[available_variables], Yvar)] |> drop_na()
      } else {
       AllData <- DD_data |> filter(Site == siteID) |> 
         filter_variables(0.8, c(variables_names_to_ids[available_variables], Xvar, Yvar))
       AllData <- AllData[,c(variables_names_to_ids[available_variables], Xvar, Yvar)] |> drop_na()
      }
      
      single_regression <- lm(as.formula(paste(Yvar, "~", Xvar)), data = BothData)
      
      correlation[index] <- summary(single_regression)$r.squared
      single_slope[index] <- summary(single_regression)$coefficients[Xvar, "Estimate"]
      
      
      multiple_regression <- lm(as.formula(paste(Yvar, "~ .")), data = AllData)
      multiple_slope[index] <- summary(multiple_regression)$coefficients[Xvar, "Estimate"]
      
      loess_regression <- loess(as.formula(paste(Yvar, "~", Xvar)), data = BothData)
      loess_RSS[index] <- sum(summary(loess_regression)$residuals ** 2)
      
    }
    index <- index + 1
  }
  df <- tibble("YearsSinceBurn" = years_since_burn, "SiteID" = site_ID, "Min" = min_val, "Max" = max_val, "Mean" = mean_val,
               "STD" = std_val, "Value With Max Flux" = val_of_max,  "Value With Min Flux" = val_of_min, 
               "Flux Correlation" = correlation, "Flux Single Regression Slope" = single_slope, 
               "Flux Multiple Regression Slope" = multiple_slope, "Flux Nearest Neighbor RSS" = loess_RSS)
  df
})
```


```{r}
#| context: server


stats_to_xlab <- reactive({
  Xvar <- input$chosenVariable2
  Yvar <- input$chosenYVariable2
  Xvar_ID <- variables_names_to_ids[Xvar]
  Yvar_ID <- variables_names_to_ids[Yvar]
  c("Min" = paste("Min of", Xvar, variables_ids_to_units[Xvar_ID]), "Max" = paste("Max of", Xvar, variables_ids_to_units[Xvar_ID]), "Mean" = paste("Mean of", Xvar, variables_ids_to_units[Xvar_ID]),
    "STD" = paste("STD of", Xvar, variables_ids_to_units[Xvar_ID]), 
    "Value With Max Flux" = paste(Xvar, "where", Yvar, "is maximum", variables_ids_to_units[Xvar_ID]),
    "Value With Min Flux" = paste(Xvar, "where", Yvar, "is minimum", variables_ids_to_units[Xvar_ID]),
    "Flux Correlation" = paste("$R^2$ Between", Xvar, "and", Yvar),
    "Flux Single Regression Slope" = paste("Single Regression Slope of", Yvar, "from", Xvar, 
                                                 variables_ids_to_units[Yvar_ID], "/", variables_ids_to_units[Xvar_ID]), 
    "Flux Multiple Regression Slope" = paste("Multiple Regression Slope of", Yvar, "from", Xvar,
                                                   variables_ids_to_units[Yvar_ID], "/", variables_ids_to_units[Xvar_ID]), 
    "Flux Nearest Neighbor RSS" = paste("RSS of Nearest Neighbor Regression of", Yvar, "from", Xvar,
                                              variables_ids_to_units[Yvar_ID]))
})

output$StatPlot <- renderPlot({
  chosen_stat <- input$chosenStat
  xlabs_dict <- stats_to_xlab()
  stats <- get_stats()
  stats |> ggplot(aes(x = YearsSinceBurn, y = !!sym(chosen_stat), color = SiteID)) + geom_point(size = 5) + 
    xlab("Years Since Burn") + scale_color_manual(labels = sites_ids_to_names, values = site_colors) +
    ylab(xlabs_dict[chosen_stat]) + theme_classic()
})


output$ViolinPlot <- renderPlot({
  siteData <- DD_data
  variable_id <- variables_names_to_ids[input$chosenVariable2]
  
  siteData |> ggplot(aes(x = Site, y = !!sym(variable_id), fill = Site)) + geom_violin() +
    scale_fill_manual(labels = sites_ids_to_names, values = site_colors) + 
    scale_x_discrete(labels = sites_ids_to_burntime) +
    labs(x = "Years Since Burn",
                 y = paste(input$chosenVariable2, variables_ids_to_units[variable_id]),
                 title = stringr::str_wrap(paste("Distribution of", input$chosenVariable2, "At All Sites"), width = title_width)) + theme_classic()
})
```

